### 2019-05-25 doc/chapters/introduction.tex
Added partially the description of Bitcoin-S to introduction.tex

% Einträge im Verzeichnis erscheinen lassen ohne hier eine Referenz einzufügen
\nocite{kopka:band1}
\nocite{raichle:bibtex_programmierung}
\nocite{MiKTeX}
\nocite{KOMA}
\nocite{TeXnicCenter}
\nocite{Marti06}
\nocite{Erbsland08}
\nocite{juergens:einfuehrung}
\nocite{juergens:fortgeschritten}

@@

%In figure \ref{fig:file_structure} the file structure is shown for this template.

%\begin{figure}[H]
%	\centering
%		\includegraphics[scale=0.85]{images/file_structure.png}
%	\caption{File structure}
%	\label{fig:file_structure}
%\end{figure}

@@

%\begin{table}[H]
%	\centering
%		\begin{tabular}{lll} \toprule
%			\textbf{First Name Last Name} & \textbf{E-mail} & \textbf{Function} \\ \midrule
%			Alfred Kaufmann & alfred.kaufmann@bfh.ch & Employer, Project Management, \\
%			& & Supplements, Improvements \\ \midrule
%			Fritz Dellsperger & Retired & Tips on the structure and layout \\ \midrule
%			David Burri & Contracted out & First compilation of the Template \\ \bottomrule
%		\end{tabular}
%	\caption{Contact Persons}
%	\label{tab:Contact Persons}
%\end{table}

@@

>>>>

@@

@@

@@

In the work some fragments of the code of Bitcoin-S will be verified. Bitcoin-S is an open source Scala implementation of the Bitcoin protocol. 
There are different projects belonging to Bitcoin-S. Protocol data structures are defined in the package \textbf{bitcoin-s-core}. This package is the main target to be verified because it specifies the base of Bitcoin protocol, and it is crucial for correct protocol functionality.
There is also the package \textbf{bitcoind-rpc} which is a RPC client implementation to communicate with \textit{bitcoind}, daemon of Bitcoin Core running on a machine.
Developers of Bitcoin-S are working on the implementation of a lightweight bitcoin client in the package \textbf{bitcoin-s-spv-node}.
